Presentation_Analysis_std

### 2023-04-15 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
update fitbit analysis

```{r}
df_ttest <- 
  main %>% 
  dplyr::select("ID","time","heart_rate_std","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ ranef(.)$ID %>% 
        as_tibble(., 
                  rownames = "ID"
                  ) %>% 
        clean_names()
      ) %>% 
  bind_rows(.,
            .id = "time_span")

main %>% 
  dplyr::select("ID","time","heart_rate_std","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ summary(.) %>% 
        .$coefficients %>% 
        .[c(1,2)]) %>% 
  bind_rows(.,
            .id = "time_span") %>% 
  pivot_longer(
  cols = everything(),
  names_to = c("diagnosis", "gender"),
  names_pattern = "new_?(.*)_(.)",
  values_to = "count"
)

t.test(df_ttest$`(Intercept)`[df_ttest$time_span == "main"],
       df_ttest$`(Intercept)`[df_ttest$time_span == "subsequent"],
       paired = TRUE)

df_ttest %>% 
  filter(time_span == "main") %>% 
  ggplot(mapping = aes(x = intercept)) +
  geom_histogram()
```

>>>>

```{r}
cache1 <- 
  main %>% 
  dplyr::select("ID","time","heart_rate_std","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ ranef(.)$ID %>% 
        as_tibble(., 
                  rownames = "ID"
                  ) %>% 
        clean_names()
      ) %>% 
  bind_rows(.,
            .id = "time_span")

cache2 <-  
  main %>% 
  dplyr::select("ID","time","heart_rate_std","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ summary(.) %>% 
        .$coefficients %>% 
        .[c(1,2)]) %>% 
  bind_rows(.,
            .id = "time_span") %>% 
  pivot_longer(
  cols = everything(),
  names_to = "time_span",
  values_to = "mean_value"
  )

df_ttest <- 
  tibble(mean_intercept = cache2$mean_value[1:6],
         mean_time = cache2$mean_value[7:12],
         time_span = cache2$time_span[1:6]) %>% 
  right_join(x = .,
             y = cache1) %>% 
  transmute(time_span,
            intercept = mean_intercept + intercept,
            time = mean_time + time)

t.test(df_ttest$intercept[df_ttest$time_span == "main"],
       df_ttest$intercept[df_ttest$time_span == "subsequent"],
       paired = TRUE)
```
